---
title: "PA1_templete"
author: "Eric Hung"
date: "2017¦~2¤ë23¤é"
output: html_document
---
#This is the assignment of Reproducible Research Week2

To start the assignment, library dplyr package first.

```{r warning=FALSE,message=FALSE}
library(dplyr)
library(ggplot2)
Sys.setlocale("LC_TIME", "English")
```


1:Code for reading in the dataset and/or processing the data. 
  
```{r echo=TRUE}
setwd("C:/Users/Eric/Documents/R/Homework/Reproducible_week2")
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",destfile = "data.zip")
unzip(zipfile = "data.zip")
temp.data <-read.csv(file = "activity.csv",header = TRUE,stringsAsFactors = FALSE)

```

2.Histogram of the total number of steps taken each day

```{r}
step.perday <- select(temp.data,c(steps,date)) %>% filter(steps!="NA") %>% group_by(date) %>% summarise(sum(steps))

hist(step.perday$`sum(steps)`,breaks = 30,col = "red", main = "Histogram of Step per Day",xlab = "Step per Day")

```

3.Mean and median number of steps taken each day

```{r}

m.perday <- select(temp.data,c(steps,date)) %>% filter(steps!="NA") %>% group_by(date) %>% summarise(mean(steps),median(steps))

names(m.perday)<- c("DATE","Mean step per day","Median step perday")

print(m.perday,n=53)

```

4.Time series plot of the average number of steps taken in each time interval
```{r}
time.data <- select(temp.data,c(steps,interval)) %>% filter(steps != "NA") %>% group_by(interval) %>% summarise(mean(steps))

plot(time.data$interval,time.data$`mean(steps)`,type="l",xlab = "Time Interval(every 5 mins)",ylab = "Average Number of Steps",main = "Time Series of Average Steps A Day",col="red")

```

5.The 5-minute interval that, on average, contains the maximum number of steps

```{r}
max.step.interval <-as.integer(subset(time.data,time.data$`mean(steps)`==max(time.data$`mean(steps)`))[,1])

```

The interval `r max.step.interval` contains the maximum number of steps

6.Code to describe and show a strategy for imputing missing data

```{r}
n.na <- nrow(temp.data[is.na(temp.data$steps),])

```
There are total `r n.na` NAs in the raw data

To imputting missing value, a average steps of each interval is used. As I believe a person's behavior is almost the same for every day.

```{r}
c.data <-temp.data
index <-which(is.na(c.data$steps))
c.data[index,1]<-time.data[match(c.data[index,3],time.data$interval),2] #to impute the missing value

```

7.Histogram of the total number of steps taken each day after missing values are imputed

```{r}
hc.data<-select(c.data,c(steps,date)) %>% group_by(date) %>% summarise(sum(steps))
hist(hc.data$`sum(steps)`,breaks = 30,col = "red", main = "Histogram of Step per Day Without Missing Value",xlab = "Step per Day")

```

Calculating the mean abd median of steps per day with missing value imputted

```{r}
mhc.data<-select(c.data,c(steps,date)) %>% group_by(date) %>% summarise(mean(steps),median(steps))
names(mhc.data)<- c("DATE","Mean step per day","Median step perday")
print(mhc.data,n=nrow(mhc.data))

```

8.Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends

```{r cache=FALSE}

weekc.data<-c.data
weekc.data$w1<-weekdays(as.Date(weekc.data$date))

weekc.data$wday<-factor(weekc.data$w1 %in% c("Monday","Tuesday","Wednesday","Thursday","Friday"),levels = c(TRUE,FALSE),labels = c("Weekday","Weekend"))

df8<-select(weekc.data,c(steps,interval,wday)) %>% group_by(interval,wday) %>% summarise(mean(steps))

names(df8) <-c("interval","wday","step")
g <-ggplot(data=df8,aes(interval,step,color=wday))
g+geom_line()+facet_wrap(~wday,ncol=1)
```

